---
name: Luisa M.
surname: Mimmi
position: Public Policy & Data Analysis
address: EU citizen (Italy) | Green card holder
www: lulliter.com
phone: +39 348 9528360 
email: lmm76@georgetown.edu
linkedin: luisa-m-mimmi
researchgate: Luisa-Mimmi
#orcid: 0000-0002-2244-8282
github: lulliter
twitter: lulliter
headcolor: 0088cc #cc0066 # 0088cc #0073e6 #990000
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: |-
  Experienced policy advisor with a strong background in statistics and econometrics applied to economic development. In over 15 years of experience in Italy and abroad, I have evaluated the feasibility and impact of policies and financial instruments promoting inclusive and sustainable access to infrastructure services (housing, mobility, water and sanitation, energy, education and health).  
  I am currently pursuing opportunities to apply my policy analysis and project management skills towards the implementation and evaluation of national & EU Structural and Investment Funds (PNRR, Next Generation EU, ERDF, ESF, CF, etc).
# aboutme: |-
#   I am an economist by training with demonstrated expertise designing and implementing diagnostic tools, advanced analytics and data visualizations applied to economic development. Most of my research revolves around different policies improving universal access to basic infrastructure services (housing, water and sanitation, energy, education and health).  
#     I am passionate about using data from different sources –including social media, GIS and satellite imagery– to understand and tackle complex public policy issues. 
profilepic: ../foto/LulaSalvador2015.jpg
docname: Curriculum Vitae
csl: apa6-cv.csl # apa-annotated-bibliography.csl
output:
  vitae::awesomecv: 
  keep_tex: false
  latex_engine: "xelatex" # maybe redund bc in awsomecv is already this 
always_allow_html: yes
header-includes:
  \usepackage{float}
  \usepackage{multicol}
  \usepackage{colortbl}
  \arrayrulecolor{white}
  \usepackage{hhline}
  \definecolor{light-gray}{gray}{0.95}
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# if (cond) expr
if (!require("pacman")) install.packages("pacman")
p_load('vitae'     # The CV's LaTeX Template
       ,'tibble'    # Data structure for tribbles
       ,'dplyr' , 'ggplot2'
       ,'lubridate'
       ,'magrittr'  # The Pipe %>%
       ,'here'      # Relative File Paths
       ,'readr'     # Data Loading
       ,'glue'      # String Manipulation
       ,'rorcid'
       ,'RefManageR'
       ,'scholar'
       , 'emojifont'
       , 'fontawesome'
       , 'ggrepel' 
       ,'kableExtra'
       ,'huxtable'
       ,'gridExtra'
)

p_load_gh("rstudio" )

 # MODO ALTERNATIVO -----------------------
# require(xfun)
# packages <- c('vitae'     # The CV's LaTeX Template
#              ,'tibble'    # Data structure for tribbles
#              ,'dplyr' 
#              ,'lubridate'
#              ,'magrittr'  # The Pipe %>%
#              ,'here'      # Relative File Paths
#              ,'readr'     # Data Loading
#              ,'glue'      # String Manipulation
#              ,'rorcid'
#              ,'RefManageR'
#              ,'scholar'
#              )
# xfun::pkg_attach2(packages, message = FALSE)
 
# data input (in "./data/data_Lula.R")   -----------------------
source(file = here::here("data", "data_Lula.R")) # "data.r"

 
# rorcid_app <- httr::oauth_app(
#   appname = "rorcid",
#   key = "APP-7E02XXWNQBFNMG1B",
#   secret = "74c15780-e323-48a0-9296-ecceaf46e447"
# )

# ORCID_TOKEN <- Sys.getenv("ORCID_TOKEN") 
```

<!-- # Employment history -->

\faIcon{briefcase} Professional Experience
============================================

```{r employment, results='asis'}
# tribble(
#   ~Years, ~Position, ~Company,
#   '2018:...', "Research Fellow", "Inter-American Development Bank, (Washington DC)",
#   '2018:...', "Fundraising Data Analyst (Pro bono)", "New York Encounter, (remote)",
#   '2009:2018', "Senior M&E Specialist", "World Bank, Sustainable Development VP, (Washington DC)",
#   '2008' , "Policy Analyst", "Inter-American Development Bank, (Washington DC)",
#   '2007' , "Summer Intern", "AVSI International (Brazil)",
#   '2001:2006', "Business Intelligence Analyst", "Value Partners (Italy)",
#    ) %>%
#   # arrange(-Years) %>%
#    #filter(Start > 2000) %>%
#   # mutate(End = replace_na(End, "")) %>%
#   # mutate(Years = paste(Start, "--", End, sep = "")) %>%
#   select(Years, Position, Company ) %>%
#   detailed_entries(
#     when = Years, 
#     what = Position, 
#     where = Company )


work %>%
  vitae::detailed_entries(
    with =  unit , #scambiati x spazio
    what = title,
    why = detail,
    when = glue::glue("{startMonth} {startYear}-{endMonth} {endYear}",.na = ""),
    where = where, #scambiati x spazio
    .protect = TRUE)

```

\newpage



<!-- # Education -->
```{r education}
# edu <- rorcid::orcid_works("0000-0002-2244-8282")
# edu$`0000-0002-2244-8282`$`education-summary` %>%
#   detailed_entries(
#     what = `role-title`,
#     when = glue::glue("{`start-date.year.value`} - {`end-date.year.value`}"),
#     with = organization.name,
#     where = organization.address.city
#   )
```

\faIcon{graduation-cap} Education
==================================
<!--  \faIcon{university} -->
```{r EDUCATION}
edu %>% 
  vitae::detailed_entries( with = inst,
    what = degree,
    why = detail,
    when =  ifelse(is.na(startYear),
                   endYear, glue::glue("{startYear}-{endYear}",.na = "")),
    where = where)
```


\faIcon{medal} Honors & Awards
=============================== 
```{r}
# ~area, ~accomplishment, ~year, ~where, [~detail],
honors %>%
  vitae::detailed_entries(
    # with = area,
    # what = accomplishment,
    what = where   ,
    when = year,
    with =glue::glue("{area} -- {accomplishment}",.na = "" )
  )
# # try to make it less pompous
# honors %>% 
#   vitae::brief_entries(
#     #with = area,
#     what = glue::glue("{area} - {accomplishment}",.na = "" )  ,
#     #why = detail,
#     when = where ,
#     with = year
#   )
```


\faIcon{laptop-code} Software
=============================== 
<!-- \faIcon{file-code} -->
  

<!-- ```{r sw_opt1} -->
<!-- # software %>% -->
<!-- #    vitae::detailed_entries( -->
<!-- #    what  = skills , -->
<!-- #     with =  area, -->
<!-- #     where = detail # -->
<!-- #   ) -->
<!-- #   -->
<!-- software %>% -->
<!--    vitae::detailed_entries( -->
<!--    what  = glue::glue("  {area}: [{skills}]") -->
<!--     #,where = detail # -->
<!--   ) -->

<!-- # software %>% -->
<!-- #    vitae::brief_entries( -->
<!-- #    what  = area , -->
<!-- #     with =  skills -->
<!-- #       -->
<!-- #   ) -->
<!-- ``` -->


```{r  sw_opt2, results='markup'}
# Lorena Abad, ma non viene !
# https://github.com/loreabad6/R-CV/blob/master/CV.Rmd

tribble(
   ~`Statistics / Databases`, ~`GIS`, ~`Other`,
  "R, RStudio, Stata, SQL, Salesforce, MS Excel",
  "ArcGIS, QGIS, GeoDa, OpenStreetMap",
  "Git, Github, Unix Shell, CSS, HTML, LaTeX, Markdown"
)  %>%
  kable(booktabs = T, align = 'c', escape = F, format = "latex")  %>%
  kable_styling(full_width = F, font_size = 10, latex_options = "HOLD_position") %>%
  row_spec(0, bold = T, color = "#009acd") |>
  row_spec(1, bold = F, color = "#7f7f7f") |>
  column_spec(column = 1:3, width = '4.75cm')
```


\faIcon{globe} Languages
==================================

<!-- ```{r lan_opt1} -->
<!-- languages %>%  -->
<!--   vitae::detailed_entries( -->
<!--     what = glue::glue("{area}: [{skills}]")  -->
<!--     ) -->
<!-- ``` -->

```{r lan_opt2, eval=FALSE, include=FALSE, results='markup'}
data.frame(
  Skill = c("Reading", "Writing", "Listening","Speaking"),
  Italian = cell_spec(c(rep("Native", 4)), 'latex', color = '#005c7b'), 
  English = cell_spec(c("C2","C2","C2","C2"), 'latex', color = '#009acd'), 
  Spanish = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#4cb8dc'), 
  Portuguese = cell_spec(c("B2","A1","B2","B2"), 'latex', color = '#4cb8dc')
  #French = cell_spec(c("A2","A1","A1","A1"), 'latex', color = '#7fcce6') 
)  %>% 
  kable(booktabs = T, align = 'c', escape = F, format = "latex")  %>% 
  kable_styling(full_width = F, font_size = 10, latex_options = "HOLD_position") %>%  
  footnote(
    footnote_as_chunk = T,
    general_title = " ",
    general = "\\\\tiny Common European Framework of Reference for Languages: A1/A2: Basic User. B1/B2: Independent User. C1/C2: Proficient User",
    escape = F
  )  %>% 
  column_spec(column = 1:6, width = '2.4cm') #|> 
  # add_header_above(' ', line = F) |>
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

```{r lan_opt3, results='markup'}
data.frame(
  Skill = c("Level"),
  Italian = cell_spec( c("Native" ), 'latex', color = '#005c7b'), 
  English = cell_spec(c("C2" ), 'latex', color = '#009acd'), 
  Spanish = cell_spec(c("C2"), 'latex', color = '#4cb8dc'), 
  Portuguese = cell_spec(c("B1"), 'latex', color = '#4cb8dc'),
  French = cell_spec(c("A1"), 'latex', color = '#7fcce6') 
)  %>% 
  kable(booktabs = T, align = 'c', escape = F, format = "latex")  %>% 
  kable_styling(full_width = F, font_size = 10, latex_options = "HOLD_position") %>%  
  footnote(
    footnote_as_chunk = T,
    general_title = " ",
    general = "\\\\tiny Common European Framework of Reference for Languages: A1/A2: Basic User. B1/B2: Independent User. C1/C2: Proficient User",
    escape = F
  )  %>% 
  column_spec(column = 1:6, width = '2.4cm') #|> 
  # add_header_above(' ', line = F) |>
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```


\faIcon{lightbulb}  Other Professional Service
===================================== 

```{r}
# service <- tribble( ~what, ~when, ~with,
#   "Peer Reviewer",                "ongoing",                   "Energy Policy & Journal of the Association of Environmental 
service %>%
  vitae::detailed_entries(
  what = what, 
  when =  when,
  why = why  
  )
  
```

<!-- \bigskip -->


\newpage

\faIcon*{pencil} Professional Development
===========================
 
```{r}
#courses <- tribble( ~area, ~accomplishment, ~year, [~where], [~detail],

courses %>%
  vitae::detailed_entries(
    #why = area ,
    what = accomplishment,
    when = year ,
    why = detail, # certificate 
    .protect = FALSE # allows links in column
  )
    
```



\faIcon{r-project}  Data Science Projects  
===================================== 

```{r PROJECTS}
# ~area,  ~year, ~accomplishment, ~where, ~link,
# projects %>%
# detailed_entries(
#     with = area,
#     when =  year,
#     what = accomplishment, 
#     # where = where,
#         why = link,
#         .protect = FALSE, # to turn link in LATEX 
#   )


#projects2 <- tibble::tribble(~name,  ~year, ~explain,
projects2 %>%
  vitae::detailed_entries(
    what = name,
    when = year,
    #with = NA_character_,
    why = explain,
    #where = NA_character_,
    .protect = FALSE
  )

```

<!-- \endfirstpage -->

<!-- FOR THESE I AM NOT ACTUALLY USING data_Lula.R [I extract from .bib directly using `vitae::bibliography_entries` own function ] -->

\newpage

\faBook[regular] Publications
===========================

\medskip

[_See detailed list on my [**Google Scholar Profile**](https://scholar.google.com/citations?user=OBYla5gAAAAJ&hl=en&oi=ao)_]

\bigskip
<!-- \medskip -->

\faBookmark[regular] Peer-Reviewed Articles
---------------------------

```{r PUBgooglesch}
# # from Google Scholar
# publicationsGSL  %>%
#   vitae::detailed_entries(
#     what = title,
#     when = year,
#     with = author,
#     where = journal #,
#     #why = glue::glue("citations: {cites}")
#   )
#     
```

```{r PUBzotero}
# # from Synched Lula-MyPublications-Narrow.bib (in Zotero)
# author, title, type, issued, journal
 
 vitae::bibliography_entries(file = here::here("data", "Lula-MyPublication-Narrow.bib")
                             # ,sorting="ydnt"
                              ) %>% 
  filter(genre == "Peer-reviewed" ) %>% 
  select(-genre) %>% 
  arrange(desc(issued)) %>% 
  filter( stringr::str_detect(type ,"webpage" , negate = TRUE)  )
 
```


\bigskip
<!-- \medskip -->

\faBookOpen[regular] Technical Reports
---------------------------

```{r TECzotero}
# # from Synched Lula-MyPublications-Narrow.bib (in Zotero)
# author, title, type, issued, journal
 
 vitae::bibliography_entries(file = here::here("data", "Lula-MyPublication-Narrow.bib")
                             # ,sorting="ydnt"
                              ) %>% 
  filter(genre != "Peer-reviewed" ) %>% 
  select(-genre) %>% 
  arrange(desc(issued)) %>% 
  filter( stringr::str_detect(type ,"webpage" , negate = TRUE)  )
 
```

\bigskip

\faIcon{rss} Other Media
---------------------------

<!-- \faIcon{file-signature} -->
```{r BLOGzotero}
# # from Synched Lula-MyPublications-Narrow.bib (in Zotero)
# author, title, type, issued, journal
 
#print<-  
vitae::bibliography_entries(file = here::here("data", "Lula-MyPublication-Narrow.bib")
                             # ,sorting="ydnt"
                              ) %>% 
     arrange(desc(issued)) %>% 
  select(-genre) %>% 
  filter( stringr::str_detect(type ,"webpage" )  )
 

# --------- names(print)
#   "URL" "author"  "genre" "id" "issued" "keyword" "language"  "publisher"  "title"            "title-short"  "type" "DOI" "ISSN" "accessed" "container-title"  "issue""page" "volume"           "abstract"  "collection-title" "number" "publisher-place"  "annote"  

# --------- print$type
# "webpage" "webpage" "report" "webpage" "webpage" "article-journal" "report"         
#  [8] "report"          "report"          "article-journal" "report"          "webpage"     
```


```{r copyTOCVDIR, message=FALSE, warning=FALSE, include=FALSE}
# here::here()
# 
# # ObjectiFY SubDirs	
# from.dir <- "./content/cv/cv_making/resume_twentysecond"
# fs::path_abs(from.dir)
# 
# to.dir   <- "./content/cv"
# fs::path_abs(to.dir)
# 
# # List Files 
# files <- list.files(path = from.dir, 
# 						  pattern='\\.pdf$', # an optional regular expression. (ends with
# 						  full.names = TRUE, # If TRUE, the directory path is prepended to the file names 
# 						  recursive = FALSE) # Should the listing recurse into directories?
# 	
# # all_munge <- list.files(path = "./03_Munge/", pattern = '\\.R$' , 
# #                         all.files = FALSE,  # def (= only visible)
# #                         full.names = FALSE, # def (= no dir name prepended)
# #                         recursive = FALSE,  # def  (= no inside sub-dir )
# #                         ignore.case = TRUE, #    (= pattern-matching be case-insensitive)
# #                         include.dirs = FALSE, # def (subdirectory names NOT be included in recursive listings)
# #                         no.. = FALSE) # def (both "." and ".." be excluded also from non-recursive listings)
# class(files) 
# 
# # function to MOVE
# for (f in files) file.copy(from = f, to = to.dir,	 overwrite = T, copy.date = T)
```


\faIcon*{microphone} Talks & Lectures
===========================
  <!-- \faIcon*{calendar} Talks  -->
```{r TALKzotero}
# # from Synched Lula-MyTalks.bib (in Zotero)
# author, title, type, issued, journal
 
  vitae::bibliography_entries(file = here::here("data", "Lula-MyTalks.bib")
                             # ,sorting="ydnt"
                              ) %>% 
  select(-genre) %>%  
  arrange(desc(issued))

```

 