---
name: Luisa M.
surname: Mimmi
#position: Public Policy & Data Analysis
address: EU citizen (Italy) | USA green card holder
www: luisamimmi.org #lulliter.com
# phone: +39 348 9528360 
email: lmm76@georgetown.edu
linkedin: luisa-m-mimmi
researchgate: Luisa-Mimmi
#orcid: 0000-0002-2244-8282
github: lulliter
#twitter: lulliter
headcolor: 0088cc #cc0066 # 0088cc #0073e6 #990000
date: "`r format(Sys.time(), '%B %Y')`"
params:
  cv_code: 
    label: cv_code
    value: pol
    input: select
    choices: ["journ","pol", "euro","data"]  
  position:
    label: position
    value: "Economist and Policy Analyst"
    input: select
    choices: ["Economist and Data Journalist","Economist and Policy Analyst", "Expert of Public Policy and EU funds planning","Public Policy & Data Analysis"]
  aboutme:
      label: Short Bio
      value: "**PROFILE**: Accomplished policy advisor with a strong background in statistics and econometrics applied to economic development. In over 15 years of experience, in Italy and abroad, I have evaluated the feasibility and impact of policies and financial instruments promoting inclusive and sustainable access to infrastructure services (housing, mobility, water and sanitation, energy, education and health). \n\n**GOAL**: I am currently pursuing opportunities to apply my policy analysis and project management skills towards the implementation and evaluation of policies for sustainable development within the national & EU context."
      input: select
      choices: ["**PROFILE**: Accomplished policy advisor with a strong background in statistics and econometrics applied to economic development. In over 15 years of experience, in Italy and abroad, I have evaluated the feasibility and impact of policies and financial instruments promoting inclusive and sustainable access to infrastructure services (housing, mobility, water and sanitation, energy, education and health). \n\n**GOAL**: I am currently pursuing opportunities to apply my policy analysis and project management skills towards the implementation and evaluation of policies for sustainable development within the national & EU context.",  
      "**PROFILE**: Accomplished policy advisor with a strong background in statistics and econometrics applied to economic development. In over 15 years of experience, in Italy and abroad, I have evaluated the feasibility and impact of policies and financial instruments promoting inclusive and sustainable access to infrastructure services (housing, mobility, water and sanitation, energy, education and health).  \n\n**GOAL**: I am currently pursuing opportunities to apply my policy analysis and project management skills towards the implementation and evaluation of national & EU Structural and Investment Funds (PNRR, Next Generation EU, ERDF, ESF, CF, Horizon, etc).", 
     "**PROFILE**: I am an economist by training with demonstrated expertise designing and implementing diagnostic tools, advanced analytics and data visualizations applied to economic development. Most of my research revolves around different policies improving universal access to basic infrastructure services (housing, water and sanitation, energy, education and health). \n\n**GOAL**: I am passionate about using data from different sources –including social media, GIS and satellite imagery– to understand and tackle complex public policy issues.", 
     "**PROFILE**: I am an economist by training with demonstrated expertise designing and implementing diagnostic tools, advanced analytics and data visualizations applied to economic development. Most of my research revolves around different policies improving universal access to basic infrastructure services (housing, water and sanitation, energy, education and health). \n\n**GOAL**: I look for opportunities to use my skills in the field of financial and economic journalism."]

# aboutme: |-
#   **PROFILE**: Accomplished policy advisor with a strong background in statistics and econometrics applied to economic development. In over 15 years of experience, in Italy and abroad, I have evaluated the feasibility and impact of policies and financial instruments promoting inclusive and sustainable access to infrastructure services (housing, mobility, water and sanitation, energy, education and health).  
#   **GOAL**: I am currently pursuing opportunities to apply my policy analysis and project management skills towards the implementation and evaluation of national & EU Structural and Investment Funds (PNRR, Next Generation EU, ERDF, ESF, CF, etc).
# aboutme: |-
#   I am an economist by training with demonstrated expertise designing and implementing diagnostic tools, advanced analytics and data visualizations applied to economic development. Most of my research revolves around different policies improving universal access to basic infrastructure services (housing, water and sanitation, energy, education and health).  
#     I am passionate about using data from different sources –including social media, GIS and satellite imagery– to understand and tackle complex public policy issues. 

#profilepic: foto/LulaSalvador2015.jpg
docname: Curriculum Vitae
csl: apa6-cv.csl # apa-annotated-bibliography.csl
output:
  vitae::awesomecv: 
  keep_tex: false
  latex_engine: "xelatex" # maybe redund bc in awsomecv is already this 
always_allow_html: yes
# from Lore Abad
header-includes:
  \usepackage{float}
  \usepackage{multicol}
  # \usepackage{hhline}
  # \definecolor{light-gray}{gray}{0.95}
  # \usepackage{colortbl}
  # \arrayrulecolor{white}
editor_options: 
  chunk_output_type: console
position: "`r params$position`" # must come AFTER the params declaration Esperta di Economia e Politiche Pubbliche
aboutme: "`r params$aboutme`" # must come AFTER the params declaration Esperta di Economia e Politiche Pubbliche
---

<!-- PARAMETRIZED WITH 3 PROFILES  -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

#install.packages('BiocManager')
#if (!require("pacman")) install.packages("pacman")
#p_load_gh("rstudio" )
library('pacman'  )  
library('vitae'  )  
library('tibble'    )  
library('dplyr' )
# library('ggplot2')
library('stringr')
library('lubridate')
library('magrittr')  
library('here'  )  
library('readr' )  
library('readxl')  
library('glue'  )  
library('rorcid')
library('RefManageR')
library('scholar')
# library('emojifont')
library('fontawesome') 
# library('ggrepel' ) 
library('kableExtra') 
# library('huxtable') 
# library('gridExtrlibrary')

 
# data input (in "./data/data_Lula.R")   -----------------------
source(file = here::here("data", "cv_data_ENG_ITA.R")) # "data.r"

# rorcid_app <- httr::oauth_app(
#   appname = "rorcid",
#   key = "APP-7E02XXWNQBFNMG1B",
#   secret = "74c15780-e323-48a0-9296-ecceaf46e447"
# )

# ORCID_TOKEN <- Sys.getenv("ORCID_TOKEN") 
```

<!-- # Employment history -->

# \faIcon{briefcase} Work Experience

 <!-- + From Microsoft .csv must be saved as CSV UTF_8 or it will mess up apostrophes -->

```{r employment, results='asis'}
## ----month in word 3 dig 
work$start_month_en <-  month.abb[work$start_month]
work$end_month_en <-  if_else(is.na(work$end_month) ,
                                    "Present", month.abb[work$end_month])
# # # 1/2 concatenate in bullets --------------
# work$detail =  Map(c, 
#                    ifelse(!is.na(work$description_1), work$description_1, NA),
#                    ifelse(!is.na(work$description_2), work$description_2, NA),
#                    ifelse(!is.na(work$description_3), work$description_3, NA)
# ) 
# 

# 2/2 concatenate in bullets [EXCEPT NA] ---------
# Create a master list, a list of lists [ie cols]
pmapinputs <- list(work$description_1, work$description_2, work$description_3)
# just 2 bullets for SHORT
pmapinputs2 <- list(work$description_1, work$description_2)

# create var -----------
work <- work %>% 
  mutate(detail_noNA =  purrr::pmap(
    pmapinputs, # a master list of all the lists we want to iterate over
    # dplyr::across(c("description_1","description_2","description_3")),
    ~ na.omit(c(...)) # na.omit returns the object with incomplete cases removed
    ),
    detail_noNA2 =  purrr::pmap(
    pmapinputs2, # a master list of all the lists we want to iterate over
    # dplyr::across(c("description_1","description_2","description_3")),
    ~ na.omit(c(...)) # na.omit returns the object with incomplete cases removed
    )
    
    )

# work$detail_noNA  

work %>%
   # fix 
  #mutate(detail = glue::glue("{description_1}, {description_2}, {description_3}",.na = "") ) %>% 
  vitae::detailed_entries(
    with =  org , #scambiati x spazio
    what = title,
    why = detail_noNA2, #detail_noNA,
    when = glue::glue("{start_month_en} {start_year}-{end_month_en} {end_year}",.na = ""),
    where = where, #scambiati x spazio
    .protect = TRUE)

```

\newpage

# \faIcon{handshake} Professional Skills
 
 •	<!-- \faIcon{calculator}--> Exceptional problem solving, critical thinking, and **data analysis skills**, showcased in international development programs    
 •	<!-- \faIcon{sitemap}--> Demonstrated drive and resourcefulness in **leadership roles** for complex projects with multiple stakeholders      
 •	<!-- \faIcon{users}--> Effective interpersonal and **communication skills**, proven by record of multilingual publications and public speaking  



# \faIcon{graduation-cap} Education

<!--  \faIcon{university} -->

```{r EDUCATION}
edu %>% 
  vitae::detailed_entries(with = inst,
         where = where,
         # qui non mi serve la durata --> extract portion before "("
         # what = str_extract(string = degree, pattern =  "^[^\\(]+" ) ,
         what =  degree ,
         when = glue::glue("{end_month} {end_year}" )
  )  
```

# \faIcon{medal} Honors & Awards

```{r}
# ~area, ~accomplishment, ~year, ~where, [~detail],
honors %>%
   vitae::detailed_entries(
    what = sponsor   ,
    when = glue::glue("{start}/{end}",.na = "" )  ,
    with = title
     )
 
```


<!-- # \faIcon*{pencil} Professional Development -->

<!-- ```{r} -->
<!-- #courses <- tribble( ~area, ~accomplishment, ~year, [~where], [~detail], -->

<!-- courses %>% -->
<!--   vitae::detailed_entries( -->
<!--     #why = area , -->
<!--     what = accomplishment, -->
<!--     when = year , -->
<!--     why = detail, # certificate  -->
<!--     .protect = FALSE # allows links in column -->
<!--   ) -->

<!-- ``` -->

<!-- # \faIcon{lightbulb} Other Professional Service -->

<!-- ```{r} -->
<!-- # service <- tribble( ~what, ~when, ~with, -->
<!-- #   "Peer Reviewer",                "ongoing",                   "Energy Policy & Journal of the Association of Environmental  -->
<!-- service %>% -->
<!--   vitae::detailed_entries( -->
<!--   what = what,  -->
<!--   when =  when, -->
<!--   why = why   -->
<!--   ) -->

<!-- ``` -->

<!-- \bigskip -->


<!-- # \faIcon{r-project} Data Science Projects -->

<!-- ```{r PROJECTS} -->
<!-- # #~area,  ~year, ~accomplishment, ~where, ~link, -->
<!-- # projects %>% -->
<!-- #   detailed_entries( -->
<!-- #     with = area, -->
<!-- #     when = year, -->
<!-- #     what = accomplishment, -->
<!-- #     # where = where, -->
<!-- #     why = link, -->
<!-- #     .protect = FALSE, # to turn link in LATEX -->
<!-- #   ) -->

<!-- # --------- better/smaller with links  -->
<!-- #projects2 <- tibble::tribble(~name,  ~year, ~explain, -->
<!-- projects2 %>% -->
<!--   vitae::detailed_entries( -->
<!--     what = name, -->
<!--     when = year, -->
<!--     #with = NA_character_, -->
<!--     why = explain, -->
<!--     #where = NA_character_, -->
<!--     .protect = FALSE -->
<!--   ) -->

<!-- ``` -->


<!-- \newpage -->

<!-- \faIcon{handshake} Personal Skills -->
<!-- ================================== -->

<!-- #### - *** COMPLETE! / TRANLSTE  -->


<!-- \faIcon{users} Competenze comunicative -->
<!-- --------------------------- -->
<!-- Esempio: -->
<!-- ▪ possiedo buone competenze comunicative acquisite durante la mia esperienza di direttore vendite -->

<!-- \faIcon{sitemap} Competenze organizzative e gestionali -->
<!-- --------------------------- -->
<!-- Esempio: -->
<!-- ▪ leadership (attualmente responsabile di un team di 10 persone) -->

<!-- \faIcon{door-open} Competenze professionali -->
<!-- --------------------------- -->
<!-- Esempio: -->
<!-- ▪ buona dei processi di controllo qualità (attualmente responsabile del controllo qualità) -->




# \faIcon{laptop-code} Software

<!-- \faIcon{file-code} -->
<!-- ```{r sw_opt1} -->
<!-- # software %>% -->
<!-- #    vitae::detailed_entries( -->
<!-- #    what  = skills , -->
<!-- #     with =  area, -->
<!-- #     where = detail # -->
<!-- #   ) -->
<!-- #   -->

<!-- software %>% -->
<!--    vitae::detailed_entries( -->
<!--    what  = glue::glue("  {area}: [{skills}]") -->
<!--     #,where = detail # -->
<!--   ) -->
<!-- # software %>% -->
<!-- #    vitae::brief_entries( -->
<!-- #    what  = area , -->
<!-- #     with =  skills -->
<!-- #       -->
<!-- #   ) -->
<!-- ``` -->

```{r  sw_opt2, results='markup'}
# Lorena Abad, ma non viene !
# https://github.com/loreabad6/R-CV/blob/master/CV.Rmd

tribble(
  ~`Office Suite`, ~`Statistics/Databases`, ~`GIS`, ~`Other`,
  "(Expert)", "(Expert)",  "(Basic)",  "(Basic)",
 "MS Office, iWork Suite, Google Suite, LibreOffice",    
   "R, RStudio, Stata, SQL, Salesforce, MS Excel",
      "ArcGIS, QGIS, GeoDa, OpenStreetMap",
        "Git, Github, Unix Shell, CSS, HTML, LaTeX, Markdown"
)  %>%
  kable(booktabs = T, align = 'c', escape = F, format = "latex")  %>%
  kable_styling(full_width = F, font_size = 10, latex_options = "HOLD_position") %>%
  row_spec(0, bold = T, color = "#009acd") %>%
  row_spec(1, bold = F, italic = T, color = "#7f7f7f") %>%
  column_spec(column = 1:4, width = '4 cm')   %>% 
# TRYING TO HAVE NO HORIZONTAL LINES  
  #row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}" ) %>% 
  #row_spec( extra_latex_after = "\\arrayrulecolor{white}")  %>%
   sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .) %>% 
  add_header_above(line = F) 
 
```

# \faIcon{globe} Languages

<!-- ```{r lan_opt1} -->
<!-- languages %>%  -->
<!--   vitae::detailed_entries( -->
<!--     what = glue::glue("{area}: [{skills}]")  -->
<!--     ) -->
<!-- ``` -->

```{r lan_opt2, eval=FALSE, results='markup'}
data.frame(
  Skill = c("Reading", "Writing", "Listening","Speaking"),
  Italian = cell_spec(c(rep("Native", 4)), 'latex', color = '#005c7b'), 
  English = cell_spec(c("C2","C2","C2","C2"), 'latex', color = '#009acd'), 
  Spanish = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#4cb8dc'), 
  Portuguese = cell_spec(c("B2","A1","B2","B2"), 'latex', color = '#4cb8dc')
  #French = cell_spec(c("A2","A1","A1","A1"), 'latex', color = '#7fcce6') 
)  %>% 
  kable(booktabs = T, align = 'c', escape = F, format = "latex")  %>% 
  kable_styling(full_width = F, font_size = 10, latex_options = "HOLD_position") %>%  
  footnote(
    footnote_as_chunk = T,
    general_title = " ",
    general = "\\\\tiny Common European Framework of Reference for Languages: A1/A2: Basic User. B1/B2: Independent User. C1/C2: Proficient User",
    escape = F
  )  %>% 
  row_spec(0, bold = T, color = "#009acd") %>% 
  column_spec(column = 1, bold = F, italic = T, color = "#7f7f7f") %>% 
  column_spec(column = 1:6, width = '2.4cm')   %>% 
# TRYING TO HAVE NO HORIZONTAL LINES  
  #row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}" ) %>% 
  #row_spec( extra_latex_after = "\\arrayrulecolor{white}")  %>%
   sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .) %>% 
  add_header_above(line = F) 
```

```{r lan_opt3, results='markup'}
data.frame(
  Skill = c( "(Written and Verbal)"), # no"  & " will mess Latex
  Italian = cell_spec( c("Native" ), 'latex', color = '#005c7b'), 
  English = cell_spec(c("C2" ), 'latex', color = '#009acd'), 
  Spanish = cell_spec(c("C2"), 'latex', color = '#4cb8dc'), 
  Portuguese = cell_spec(c("B1"), 'latex', color = '#4cb8dc'),
  French = cell_spec(c("A1"), 'latex', color = '#7fcce6') 
)  %>% 
  kable(booktabs = T, align = 'c', escape = F, format = "latex")  %>% 
  kable_styling(full_width = F, font_size = 10, latex_options = "HOLD_position") %>%  
  footnote(
    footnote_as_chunk = T,
    general_title = " ",
    general = "\\\\tiny Common European Framework of Reference for Languages: A1/A2: Basic User. B1/B2: Independent User. C1/C2: Proficient User",
    escape = F
  )  %>% 
  row_spec(0, bold = T, color = "#009acd") %>% 
  column_spec(column = 1, bold = F, italic = T, color = "#7f7f7f") %>% 
  column_spec(column = 1:6, width = '2.4cm')   %>% 
# TRYING TO HAVE NO HORIZONTAL LINES  
  #row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}" ) %>% 
  #row_spec( extra_latex_after = "\\arrayrulecolor{white}")  %>%
   sub("\\\\toprule", "", .) %>%
  sub("\\\\bottomrule", "", .) %>% 
  add_header_above(line = F) 
```


<!-- \endfirstpage -->

<!-- FOR THESE I AM NOT ACTUALLY USING data_Lula.R [I extract from .bib directly using `vitae::bibliography_entries` own function ] -->
 
# \faBook[solid] Publications


<!-- #### - *** [links outside of page... apa style issues] -->

<!-- ## \faIcon{paperclip} Peer-Reviewed Articles -->

```{r PUBzotero,  eval=FALSE}
# # from Synched Lula-MyPublications-Narrow.bib (in Zotero)
# author, title, type, issued, journal

 vitae::bibliography_entries(file = here::here("data", "Lula-MyPublication-Narrow.bib")
                             # ,sorting="ydnt"
                              ) %>%
  filter(genre == "Peer-reviewed" ) %>%
  select(-genre) %>%
  arrange(desc(issued)) %>%
  filter( stringr::str_detect(type ,"webpage" , negate = TRUE)  )

```

<!-- \bigskip -->

## \faBookOpen[solid] Peer-reviewed Articles and Technical Reports

```{r TECzotero,  eval=FALSE}
# # from Synched Lula-MyPublications-Narrow.bib (in Zotero)
# author, title, type, issued, journal
 
 vitae::bibliography_entries(file = here::here("data", "Lula-MyPublication-Narrow.bib")
                             # ,sorting="ydnt"
                              ) %>% 
  filter(genre != "Peer-reviewed" ) %>% 
  select(-genre) %>% 
  arrange(desc(issued)) %>% 
  filter( stringr::str_detect(type ,"webpage" , negate = TRUE)  )
 
```

\textcolor{cyan}{\href{https://scholar.google.com/citations?user=OBYla5gAAAAJ&hl=en&oi=ao)}{[See  \textbf{Google Scholar profile}]}} 

\medskip

## \faIcon{rss} Other Media

<!-- \faIcon{file-signature} -->
\textcolor{cyan}{\href{https://lulliter.com/publications.html\#misc.-divulgative-pieces}{[See \textbf{personal website}]}} 


```{r BLOGzotero, eval=FALSE}
# # from Synched Lula-MyPublications-Narrow.bib (in Zotero)
# author, title, type, issued, journal

vitae::bibliography_entries(file = here::here("data", "Lula-MyPublication-Narrow.bib")
                             # ,sorting="ydnt"
                              ) %>% 
     arrange(desc(issued)) %>% 
  select(-genre) %>% 
  filter( stringr::str_detect(type ,"webpage" )  )
```

# \faIcon*{microphone} Talks & Lectures

<!-- \faIcon*{calendar} Talks  -->

```{r TALKzotero, eval=FALSE}
# # from Synched Lula-MyTalks.bib (in Zotero)
# author, title, type, issued, journal
vitae::bibliography_entries(file = here::here("data", "Lula-MyTalks.bib")
                            # ,sorting="ydnt"
) %>% 
  select(-genre) %>%  
  arrange(desc(issued))
```

\textcolor{magenta}{\href{https://lulliter.com/publications.html\#selected-presentations}{[See \textbf{personal website}]}} 

<!-- \vspace*{\fill} -->
<!-- \footnotesize \textcolor{lightgray}{Autorizzo il trattamento dei miei dati personali presenti nel curriculum vitae ai sensi del Decreto Legislativo 30 giugno 2003, n. 196 e del GDPR (Regolamento UE 2016/679).}  -->


